### 2022-05-24 Manuscript/Manuscript.tex
Clarify appendices

\textit{\textbf{Example}: See lines 2 - 10 in the \nameref{S2_Appendix} for the corresponding JSON..}

@@

\paragraph*{S2 Appendix.}
\label{S2_Appendix}
{\bf Pokémon key example.} A Clavis-compliant key to a number of Pokémon, used to illustrate the different aspects Clavis supports.

\paragraph*{S3 Appendix.}
\label{S3_Appendix}
{\bf Titmice key example.} A Clavis-compliant key to Norway's titmice (Paridae). Serves as a real life example using only the aspects of Clavis it needs.

>>>>

\textit{\textbf{Example}: See lines 2 - 10 in the \nameref{S2_Appendix} for the corresponding JSON.}

@@

\paragraph*{S2 Appendix.}
\label{S2_Appendix}
{\bf Pokémon key example.} A Clavis-compliant key to a number of Pokémon. Serves to illustrate all the different aspects that Clavis supports, rather than to provide a fully functional and complete key.

\paragraph*{S3 Appendix.}
\label{S3_Appendix}
{\bf Titmice key example.} A Clavis-compliant key to Norway's titmice (Paridae). Serves as a real life example of a fully functional and complete key, using only a selection of Clavis' capabilities.
